\name: Deterministic and Coherent Implicits

### 2017-02-27 src/Conclusion.tex
add conclusion

Our main contribution is the development of the implicit
calculus $\ourlang$. This calculus isolates and formalizes the key
ideas of Scala implicits and provides a simple model for language designers 
interested in developing similar mechanisms for their own languages. 
In addition, $\ourlang$ supports higher-order rules and partial resolution, 
which add considerable expressiveness to the calculus.

Implicits provide an interesting alternative to conventional GP 
mechanisms like type classes or concepts. By decoupling resolution 
from a particular type of interfaces, implicits make resolution 
more powerful and general. Furthermore, this decoupling has other benefits too. 
For example, by modeling concept interfaces as conventional types, those interfaces can 
be abstracted as any other types, avoiding the issue of second class interfaces 
that arise with type classes or concepts.

Ultimately, all the expressiveness offered by $\ourlang$
offers a wide-range of possibilities for new generic programming applications.

>>>>

This paper has presented $\ourlang$, the Calculus Of CoHerent ImplicitS, a new
calculus for implicit programming that improves upon the implicit calculus and
strikes a good balance between flexibility and coherence. In particular,
$\ourlang$ supports local scoping, overlapping instances, first-class
instances, and higher-order rules, while remaining type safe, coherent and
unambiguous.

In future work it would be interesting to integrate Genus's solution for the
global coherence problem~\cite{Zhang15LFO}.
